---
title: "Exploratory Data Analysis Week One"
author: "Sagnik Das"
date: "6/2/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exploratory Graphics Part-1:Week-1


```{r}
setwd("C:\\Users\\das90\\OneDrive\\Coursera courses\\John Hopkins\\R Codes and Files\\Data-Science-Specialization-with-R-Exploratory-Data-Analysis")


```

### Exploratory Graphs:Part-1

```{r}

pollution<- as.data.frame(read.csv("C:\\Users\\das90\\OneDrive\\Coursera courses\\John Hopkins\\R Codes and Files\\Exploratory Data Analysis\\PM25data\\data\\avgpm25.csv"))
head(pollution)
names(pollution)

```
The national average for pm25 is 12 micrograms. We want to see for how many counties the pm25 exceeds the national average.

First we check the summary statistics of the variable we are concerned with:

```{r}
summary(pollution$pm25)

```


To visualize the data graphically, we can use multiple methods.

First let us visualize it using a simple boxplot.

```{r}

boxplot(pollution$pm25,col = "blue")

```

Now we can plot a histogram for the same data.

```{r}
hist(pollution$pm25,breaks = 100,col = "red") 
rug(pollution$pm25)

```
 Now we will look at how to plot 2 dimensional data. The following is a simple boxplot of the variable pm25, plotted over regions:
 
 
```{r}
 
boxplot(pm25~region,data=pollution,col="green") 
 
``` 

Now we will plot the same data using multiple histograms:


```{r}
par(mfrow = c(2,1))
hist(subset(pollution,region=="east")$pm25,breaks = 100,col = "blue")
hist(subset(pollution,region=="west")$pm25,breaks = 100,col = "blue")

```


### Scatter Plot

Now we will use the data to do some scatter plots:

```{r}
with(pollution,plot(latitude,pm25))
abline(h=12,lwd=2,lty=3)

```

We can use the color option to have a different colour for the scatter for different regions.

```{r}

with(pollution,plot(latitude,pm25,col=c("red","blue")))
abline(h=12,lwd=2,lty=3)

```


Let us now do a multiple scatterplot. A scatter for each region.

```{r}

par(mfrow=c(1,2), mar=c(5,4,2,1))
with(subset(pollution,region=="west"), plot(latitude,pm25,main = "west"))
with(subset(pollution,region=="east"), plot(latitude,pm25,main = "east"))


```


### Using the Base Plotting System


```{r}

df<-datasets::cars
with(df, plot(speed,dist))
```

### Using the Lattic Plotting System


```{r}
install.packages("lattice")
library(lattice)

xyplot(pm25~latitude|region,data = pollution,layout=c(2,1))
```

###Using ggplot2

```{r}
install.packages("ggplot2")
library(ggplot2)

cars= datasets::mtcars
names(cars)
qplot(mpg,disp,data=cars)
```

### Base Plotting System: A detailed look at the Base Plotting System


Let us start with a simple Histogram:


```{r}
library(datasets)
hist(airquality$Ozone)

```

Let us now loot at a simple scatter plot:


```{r}

with(airquality,plot(Wind,Ozone))

```

Now we will look at how to do a Boxplot by using a factor variable.

```{r}
airquality<- transform(airquality,Month=factor(Month))
boxplot(Ozone~Month,airquality,xlab = "Month",ylab = "Ozone(ppb)")


```


Let us now see how to add a title to a base plot:

````{r}
with(airquality,plot(Wind,Ozone))
title(main = "Ozone and Wind in New York City")

```

Now let us plot the same base plot with more annotattions.

```{r}
with(airquality,plot(Wind,Ozone), main = "Ozone and Wind in New York City")
with(subset(airquality,Month==5), points(Wind,Ozone,col="blue"))


```

Now let us add further annotations like label and legends:


```{r}
with(airquality,plot(Wind,Ozone), main = "Ozone and Wind in New York City",type="n")
with(subset(airquality,Month==5), points(Wind,Ozone,col="blue"))
with(subset(airquality,Month!=5), points(Wind,Ozone,col="red"))
legend("topright", pch = 1,col = c("blue", "red"), legend = c("May", "Other Months"))
```

Now we look at a base plot with a regression line:

```{r}
with(airquality,plot(Wind,Ozone, main = "Ozone and Wind in New York City",pch=20))
model<- lm(Ozone~Wind,airquality)
abline(model,lwd=2)


```

Plotting multiple base plots:

```{r}
names(airquality)
par(mfrow=c(1,2))
with(airquality,{
  plot(Wind,Ozone,main = "Ozone and Wind")
  plot(Solar.R,Ozone,main = "Ozone and Solar Radiation")
})


```

Adding further annotations:

```{r}
par(mfrow=c(1,3), mar=c(4,4,2,1), oma=c(0,0,2,0))
with(airquality,{
  plot(Wind,Ozone,main = "Ozone and Wind")
  plot(Solar.R,Ozone,main = "Ozone and Solar Radiation")
  plot(Temp,Ozone,main = "Ozone and Temperature")
  mtext("Ozone and weather in New York City", outer=TRUE)
})


```

### Using Graphics Devices


Now we will learn how to use the different graphic devices of R:

```{r}
pdf(file = "Plot1 Week 1.pdf")
par(mfrow=c(1,3), mar=c(4,4,2,1), oma=c(0,0,2,0))
with(airquality,{
  plot(Wind,Ozone,main = "Ozone and Wind")
  plot(Solar.R,Ozone,main = "Ozone and Solar Radiation")
  plot(Temp,Ozone,main = "Ozone and Temperature")
  mtext("Ozone and weather in New York City", outer=TRUE)
})


```





