---
title: 'Exploratory Data Analysis: Week 2;Codes'
author: "Sagnik Das"
date: "6/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Lattice Plotting System


Let practice some plotting with the lattice package:

We start with a very simple example.


```{r}

library(datasets)
library(lattice)

df<- datasets::airquality

xyplot(Ozone~Wind, data = df)

```

Now let us do a more complex graph with multiple panels:


```{r}

table(df$Month)

```

So we have 5 months of data and we want to see the relationship between Ozone and Wind for the 5 months separetly and we want to plot the data in one panel.

In order to do that, we first need to transform the month variable into a factor variable. The following codes does that:

```{r}
airquality<- transform(airquality,Month=factor(Month))


```

Now we cal get the plot we want:


```{r}

xyplot(Ozone~Wind|Month,data = airquality,layout=c(5,1))

```

Now let us plot a lattice graph over two panel. In order to do that we are going to generate some data. The following are the codes to generate the data:

```{r}
set.seed(10)
x<-rnorm(100)
f<-rep(0:1,each=50)
y<- x+f-x*f+rnorm(100,sd=0.6)
f<- factor(f,labels = c("Group1","Group2"))

```


Now let us plot the data over two panels:


```{r}

xyplot(y~x|f, layout=c(2,1))


```


Let us now plot the same graph with a bit more customization. Basically what we want to do is add a horizontal line through the median of the two datasets contained in the two panels. The code to do is given as follows:


```{r}
xyplot(y~x|f, panel = function(x,y,...){
  
  panel.xyplot(x,y,...)
  panel.abline(h=median(y), lty=3)

})


```

In the same graph, suppose we want to plot a regression line through the graphs instead of a horizontal line. The code to do that is as follows:


```{r}
xyplot(y~x|f, panel = function(x,y,...){
  
  panel.xyplot(x,y,...)
  panel.lmline(x,y,col=2)

})


```


